All MMs and AMCEs

### 2023-09-08 notebook/results.qmd
Sum the epreds for categories 1-3 instead of inverting 0

tar_load(c(preds_conditional_treatment_only, grid_treatment_only))
tar_load(c(level_lookup, feature_lookup))

@@

```{r calc-mms}
preds_all <- preds_conditional_treatment_only %>% 
  filter(.category == 0) %>% 
  mutate(.epred = 1 - .epred)

mms_org <- preds_all %>% 
  group_by(feat_org, .draw) %>% 
  summarize(avg = mean(.epred))

>>>>

tar_load(c(grid_treatment_only, level_lookup, feature_lookup))
preds_all <- tar_read(preds_conditional_treatment_only)

@@

```{r calc-mms}
mms_org <- preds_all %>% 
  group_by(feat_org, .draw) %>% 
  summarize(avg = mean(.epred))
